Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/wg_main_publishing_SW.tex
A few more changes that seem to make sense.

\textbf{Reproducibility}: Part of the purpose of these executable paper venues
is to (at least partially) address the reproducibility issue by making paper
recompute their own results.

\textbf{Software Credit (\S\ref{sec:software-credit})}: Since these forms of
publishing must make their sources explicit in order to execute, they should be
easier to trace even if appropriately worded credit for software is not
provided. In addition, some software notebooks (i.e., active or executable papers; 
see Appendix~\ref{sec:appendix_publishing_SW} for examples) 
make it possible to provide or define
additional metadata to make the tracing of credit clearer. Finally, attributions
could be added to citations to identify whether a paper extends a result,
verifies it, contradicts it, etc.

\textbf{Best Practices (\S\ref{sec:best-practices})}: Because an executable
paper showcases the code, and the code itself is subject to the review process,
authors are more likely to pay attention to coding practices. In addition,
because the paper must explain what the code does, better documentation is
more likely to be achieved.

>>>>

\begin{itemize}
\item \textbf{Reproducibility}: Part of the purpose of these executable paper venues
is to (at least partially) address the reproducibility issue by making papers
recompute their own results.

\item\textbf{Software Credit (\S\ref{sec:software-credit})}: Since these forms of
publishing must make their sources explicit in order to execute, they should be
easier to trace even if appropriately worded credit for software is not
provided. In addition, some  notebooks, i.e., active or executable papers,
(see Appendix~\ref{sec:appendix_publishing_SW} for some concrete examples) 
make it possible to provide or define
additional metadata to make the tracing of credit clearer. Finally, attributions
could be added to citations to identify whether a paper extends a result,
verifies it, contradicts it, etc.

\item \textbf{Best Practices (\S\ref{sec:best-practices})}: Because an executable
paper showcases the code, and the code itself is subject to the review process,
authors are more likely to pay attention to coding practices. In addition,
because the paper must explain what the code does, better documentation is
more likely to be achieved.
\end{itemize}
